---
title: "01"
format: pdf
editor: visual
---

## mlr3

Please head to https://github.com/mlr-org/mlr3 which has several useful links in the README.

## Prerequisite

```{r}
install.packages("mlr3verse")
install.packages("usethis")
```

We recommend adding the mlr-org R-universe to your R options so you can install all packages with install.packages(), without having to worry which package repository it comes from. To do this, install usethis and run the following:

```{r}
#| echo: false
usethis::edit_r_profile()
```

As well as packages within the mlr3 ecosystem, software in the mlr3verse also depends on the following popular and well-established packages:

-   R6

-   data.table

-   digest

-   uuid

-   lgr

-   mlbench

-   evaluate

-   future

### `data.table` for beginners

```{r}
library(data.table)
as.data.table(matrix(runif(4), 2, 2))
```

```{r}
dt = data.table(x = 1:6, y = rep(letters[1:3], each = 2))
dt
```

```{r}
dt[, mean(x), by='y']
```

```{r}
dt[, z := x * 3]
dt
```
